---
title: "Final Project Report"
author: "Daniel Seok Lee"
date: "May 4, 2021"
output: html_notebook
---

How well are the players performing after signing multi-year contracts for millions of dollars?

Over the years, the NBA has been bringing in more revenue. This raises the net worth of teams which allows them to sign better players and bigger contracts. While the average player brings in a good amount of money, a superstar will sign multi-year contracts for millions of dollars. 

In the summer of 2019, an NBA star, named Rudy Gobert, signed a five-year $205 million contract extension with the Utah Jazz. Shaquille O'Neal criticized Gobert's game and claimed that he's not worth that much. 

I will investigate how well the top-earners of the league are performing compared to the rest of the league. I will use in-game statistics to determine the performance of the players to see if they are worth the money.

```{r}
#Set up
library(readr)
library(dplyr)
library(mosaic)
library(tidyverse)
library(ggplot2)
library(esquisse)
```

```{r}
#Reading in data files
NBA2020_2021Salaries <- read_csv("NBA2020:2021Salaries.csv")

NBAStats <- read_csv("NBAStats.csv")

StatsfromNBA <- read_csv("StatsfromNBA.csv")

Top50ofNBA <- read_csv("Top50ofNBA.csv")
```

```{r}
#Summary
summary(NBA2020_2021Salaries)
```

```{r}
#Summary
summary(NBAStats)
```
```{r}
NBA2020_2021Salaries %>%
  summarise(avgsal = mean(Salary, na.rm = TRUE))
```
```{r}
NBAStats %>%
  summarise(avgpts = mean(PTS, na.rm = TRUE),
            avgast = mean(AST, na.rm = TRUE),
            avgtrb = mean(TRB, na.rm = TRUE))
```
From the summarizes of these two tables, we can see that the average player is paid $6,752,150 for the season. The average player gets 8.6 points, 1.9 assists, and 3.6 rebounds.

```{r}
#Joining stats and salary of top 50 players
Top50 <-
  Top50ofNBA %>%
  select(Player, PTS, REB, AST, EFF) %>%
  left_join(NBA2020_2021Salaries %>% select(Player, Salary), by = c("Player" = "Player"))

#Average of top 50
Top50 %>%
  summarise(avgpts = mean(PTS, na.rm = TRUE),
            avgast = mean(AST, na.rm = TRUE),
            avgreb = mean(REB, na.rm = TRUE),
            avgeff = mean(EFF, na.rm = TRUE),
            avgsal = mean(Salary, na.rm = TRUE))
```
From the averages of the Top 50, we can see that they are scoring near triple the average points, making more than double the average assists, and getting nearly double the assists. For the 2021 season, the Top 50 makes about triple of the average player. 

In the middle of the NBA season, the league holds an All-Star Break. One of the events and the biggest one is the All-Star game. This game involves about 24 of the top players of the league. Captains are chosen through voting by the fans. So let's see how the top 22 compare to the rest of the league statistically. 

Efficiency is calculated by the formula: (PTS + REB + AST + STL + BLK − Missed FG − Missed FT - TO) / GP. It is used to determine how well a player is playing and who deserves to be crowned MVP at the end of the regular season.

```{r}
Top22 <-
  Top50ofNBASal %>%
    filter(EFF > 22.75) %>%
    arrange(desc(EFF))
Top22
```
So I filtered the data so that we only get players whose efficiency are better than the average Top 50, 22.75.

Just from looking at the top 10, we can see that Luka Doncic isn't being paid as much and the rest of the players. And Rudy Gobert isn't even on the list. 

Shaquille O'Neal may have a point when he says that Rudy Gobert is not worth that much.

```{r}
TopPlayers <- 
  Top22 %>%
    filter( PTS > 10, REB > 10, AST > 8)

TopPlayers %>%
  pivot_longer(!Player, names_to = "Stat", values_to = "count")
```
This table shows some of the best rounded players and who to build a team around. 