---
title: "Final Project Report"
author: "Daniel Seok Lee"
date: "May 4, 2021"
output: html_notebook
---

How well are the players performing after signing multi-year contracts for millions of dollars?

Over the years, the NBA has been bringing in more revenue. This raises the net worth of teams which allows them to sign better players and bigger contracts. While the average player brings in a good amount of money, a superstar will sign multi-year contracts for millions of dollars. 

In the summer of 2019, an NBA star, named Rudy Gobert, signed a five-year $205 million contract extension with the Utah Jazz. Shaquille O'Neal criticized Gobert's game and claimed that he's not worth that much. 

I will investigate how well the top-earners of the league are performing compared to the rest of the league. I will use in-game statistics to determine the performance of the players to see if they are worth the money.

```{r}
#Set up
library(readr)
library(dplyr)
```

```{r}
#Reading in data files
NBA2020_2021Salaries <- read_csv("NBA2020:2021Salaries.csv")

NBAStats <- read_csv("NBAStats.csv")

StatsfromNBA <- read_csv("StatsfromNBA.csv")

Top50ofNBA <- read_csv("Top50ofNBA.csv")
```

```{r}
#Summary
summary(NBA2020_2021Salaries)
```

```{r}
#Summary
summary(NBAStats)
```
```{r}
NBA2020_2021Salaries %>%
  summarise(avgsal = mean(Salary, na.rm = TRUE))
```
```{r}
NBAStats %>%
  summarise(avgpts = mean(PTS, na.rm = TRUE),
            avgast = mean(AST, na.rm = TRUE),
            avgtrb = mean(TRB, na.rm = TRUE))
```
From the summarizes of these two tables, we can see that the average player is paid $6,752,150 for the season. The average player gets 8.6 points, 1.9 assists, and 3.6 rebounds.

In the middle of the NBA season, the league holds an All-Star Break. One of the events and the biggest one is the All-Star game. This game involves about 25 of the top players of the league. So let's see how the top 25 compare to the rest of the league statistically.

```{r}
#Joining stats and salary of top 50 players
Top50ofNBASal <-
  Top50ofNBA %>%
  select(Player, PTS, REB, AST, EFF) %>%
  left_join(NBA2020_2021Salaries %>% select(Player, Salary), by = c("Player" = "Player"))

# %>% arrange(desc(PTS))

#Average of top 50
Top50ofNBASal %>%
  summarise(avgpts = mean(PTS, na.rm = TRUE),
            avgast = mean(AST, na.rm = TRUE),
            avgreb = mean(REB, na.rm = TRUE),
            avgeff = mean(EFF, na.rm = TRUE),
            avgsal = mean(Salary, na.rm = TRUE))
```

